---
title: "Mixture Model with mclust"
author: "Christophe Ambroise"
date: "22/10/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The `mclust` package

For more details on using `mclust` see  [the mclust vignette](https://www.stat.washington.edu/sites/default/files/files/reports/2012/tr597.pdf).


## Univariate mixture


 Simulate  a sample of size 1000 of a  one dimensional mixture of two gaussians with respective means, variances and proportions
    $\mu_1=0$, $\mu_2=4$ $\sigma_1=1$,  $\sigma_2=\frac{1}{2}$, $\pi_1=\frac{1}{3}$.
    
```{r}
nks<-rmultinom(1,1000,prob = c(1/3,2/3))
means<-c(0,4)
sds<-c(1,1/2)
samples <- mapply(function(nk,mean,sd){rnorm(nk,mean,sd)},
                  nks,
                  means,
                  sds)
hist(x<-unlist(samples))

curve(dnorm(x,mean=4,sd=1/2),-2,7,col="blue")
curve(dnorm(x,mean=0,sd=1),-2,7,col="orange",add=TRUE)

mixture<-function(x){
  1/3* dnorm(x,mean=0,sd=1)+
  2/3* dnorm(x,mean=4,sd=1/2) 
    }
curve(mixture(x),-2,7,col="red",add=TRUE)

res.kmeans<-kmeans(x,2,nstart = 10)
list.of.cluster<- split(data.frame(x),res.kmeans$cluster)
mapply(function(cluster){paste("mean:", mean(cluster[[1]]),
                                "sd: ",sd(cluster[[1]]),"\n")},list.of.cluster)
```
    

## Bivariate gaussian

```{r}
library(mclust)
data("faithful")
plot(faithful)
```
The data visually display two main groups of eruptions. 

Let us run `mclust`
```{r}
faithfulMclust <- Mclust(faithful)
summary(faithfulMclust)
```

In the case of the best model chosen with BIC, the parameters are:
```{r}
summary(faithfulMclust, parameters = TRUE)
```

```{r}
plot(faithfulMclust)
```

- The classification is obtained via the MAP
- The uncertainty in the classification associated with conditional probabilities z can be obtained by subtracting the probability of the most likely group for each observation from 1



```{r}
res.hclust<-hclust(dist(faithful), method="ward.D2")
plot(res.hclust)
cutree(res.hclust,3)->hclust.3.clustering
cutree(res.hclust,2)->hclust.2.clustering
mclust.3.clustering<-Mclust(faithful,3)
mclust.2.clustering<-Mclust(faithful,2)
```

```{r}
table(mclust.2.clustering$classification,hclust.2.clustering)
table(mclust.3.clustering$classification,hclust.3.clustering)
```

Allmost identical results for 2 cluster, but very different results for 3 clusters. 

